Thermal relaxation is important in convective simulations: \\ on the time evolution of flows and how to avoid unnecessary thermal rundown

### 2020-02-15 tex/mixedft_evolution_ms.tex
good second draft of paper complete

\begin{abstract}
Astrophysical studies of convection often impose different thermal boundary conditions at the top and the bottom of the domain in an effort to more accurately reflect the natural system being modeled.
In this work, we study \RB convection (RBC) to show that the use of these mixed thermal boundary conditions imposes a long thermal rundown on convective systems which is not experienced by the more classical system where the temperature is fixed at the top and bottom of the domain.
We demonstrate that the mean behavior of an evolved simulation with mixed thermal boundaries corresponds to an equivalent simulation with fixed temperature boundaries at the top and bottom.
We show that the fast evolution of fixed-temperature simulations can be taken advantage of to rapidly relax simulations with mixed boundaries.
In the measurements presented here, we find that the asymmetries created by mixed boundaries do not importantly affect spatially averaged dynamics, but we do find that more extreme values of temperature can occur near a fixed flux boundary than a fixed temperature boundary.
We also demonstrate that these findings carry over to more complicated problems through a brief examination of rotating convection.
These results suggest that thermal relaxation occurs in two stages: (1) changes to the experimental energy reservoir and (2) changes to the stratification of the experiment.
Through the proper choice of boundary conditions or initial conditions, the first of these stages can be bypassed, and the second stage seems to be irrelevant for RBC.
\end{abstract}
\maketitle

@@

\section{Introduction}
\label{sec:introduction}
Convection is a crucial heat transport mechanism in the atmospheres and interiors of stars and planets.
The nature of astrophysical convection is primarily studied through the use of numerical simulations which range from studies of the highly simplified Boussinesq approximation \cite{spiegel&veronis1960} to more complex ``dynamo simulations'' which include magnetism and atmospheric density stratification \cite{charbonneau2014, toomre2019}.
Regardless of the degree of apparent realism of the employed simulations, numerical convection is fundamentally driven by some combination of imposed boundary conditions and internal heating profiles \cite{goluskin2015}.
A common choice of thermal boundary conditions in astrophysical convection \cite{glatzmaier&gilman1982, hurlburt&all1986, cattaneo&all1990, featherstone&hindman2016a, korre&all2019, wood&brummell2018, kapyla&all2019} is to fix the flux at the bottom boundary and to fix the value of a thermodynamic quantity (e.g., temperature) at the top boundary.
In this work, we will examine the consequences of these ``mixed'' boundaries in the simplest possible model: \RB convection (RBC) under the Boussinesq approximation.
In this model, temperature is the only thermodynamic quantity and we use the term ``FT'' boundaries to refer to the choice of fixing the flux at the bottom and the temperature at the top of the simulation.

Despite FT boundary conditions being frequently used, we are unaware of any study which has aimed to understand the consequences of imposing FT boundaries compared to the most classic RBC setup where the temperature is fixed at the top and bottom (hereafter ``TT'' boundaries\footnote{Note, in ref.~\cite{goluskin2015}, our TT and FT are repsectively called RB1 and RB3.}).
It is generally assumed that FT boundaries should behave fundamentally similarly to a system in which the flux is fixed at both boundaries (hereafter ``fixedF'' boundaries), whose behavior is well-known \cite{otero&all2002, goluskin2015}.
FixedF and TT boundaries have been shown to produce the same scaling of heat transport as the convective is ddriven more strongly \cite{johnston&doering2009}, and it is natural to assume that FT should fall on the same scaling laws.
However, the choice of FT boundaries introduces complexities into the convective system which neither fixedF or TT boundaries are exposed to.
First, the evolved mean temperature of a simulation with FT boundaries differs from the initial mean temperature, and therefore the thermal reservoir of the convective system must evolve over time.
Second, FT boundary conditions are fundamentally asymmetric, and the degree to which these boundary conditions break the symmetry of the system is unclear.

In this paper, we investigate the time evolution and nature of asymmetries in \RB covection when FT boundary conditions are imposed.
We also compare the flows in evolved, thermally relaxed FT simulations to the flows in evolved TT simulations.
We find that the thermal evolution and relaxation of FT systems is very long compared to TT systems, where it is nearly instantaneous.
However, this long thermal evolution can be bypassed by using the results of TT simulations as initial conditions for FT simulations.
If a FT simulation is allowed to relax through its natural thermal rundown, these simulations perform a sweep through parameter space where the dynamical nature of the early flows are very different from those of the relaxed flows.
Our results also suggest that the choice of FT boundaries imposes some asymmetries on the convective flows, but that these asymmetries do not change the mean convective state when compared to TT siulations.
We present these findings as follows.
In section \ref{sec:simulations}, we describe our simulation setup and numerical methods.
In section \ref{sec:2d_results}, we first describe our findings with respect to the time evolution of FT systems, and then describe the asymmetries in these systems.
In section \ref{sec:rotating_results}, we show that these findings carry over to a more complex system: rotating \RB convection.
Finally, in section \ref{sec:discussion}, we summarize our findings and briefly describe the implications of this work for the field of astrophysical convection.

@@

\section{Simulation Details}
\label{sec:simulations}
We study incompressible \RB convection under a freefall nondimensionalization as we have done previously \cite{anders&all2018}; for details of the nondimensionalization, we refer readers to that previous work.
In section \ref{sec:rotating_results} we study convection which includes the effects of vertical global rotation \cite{julien&all1996}, so here we include the Coriolis term in the momentum equation for generality.
The equations of motion are
\begin{align}
\Div{\bm{u}} &= 0
	\label{eqn:incompressible}
\\
\frac{\partial \bm{u}}{\partial t} + \left(\bm{\omega} + \frac{1}{\text{Ek }\Reff}\hat{z}\right)\times\bm{u} 
&= - \grad \varpi + T_1\hat{z} - \frac{1}{\Reff}\grad\times\bm{\omega},
	\label{eqn:bouss_momentum}
\\
\frac{\partial T_1}{\partial t}  + \bm{u}\cdot\grad T_1 + w \frac{\partial T_0}{\partial z} 
&= \frac{1}{\Peff}\grad^2 T_1,
	\label{eqn:bouss_energy}
\end{align}
where $\bm{u} = (u, v, w)$ is the velocity, $T = T_0(z) + T_1(x, y, z, t)$ is the temperature (where $T_0$ is the initial profile and $T_1$ is the fluctuations around that profile), $\varpi$ is the reduced kinematic pressure \cite{anders&all2018} which enforces the incompressible constraint, and $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.
The dimensionless control parameters are the Rayleigh, Prandtl, and Ekman numbers,
\begin{equation}
\text{Ra} = \frac{g \alpha L_z^3 \Delta}{\nu\kappa} = \frac{(L_z\,v_{\text{ff}})^2}{\nu\kappa}, \qquad \text{Pr} = \frac{\nu}{\kappa}, \qquad \text{Ek} = \sqrt{\frac{\nu}{2\Omega L_z^2}},
\end{equation}
where $g$ is the gravity, $\alpha$ is the coefficient of thermal expansion, $L_z$ is the domain depth, $\nu$ and $\kappa$ are respectively the viscous and thermal diffusivity, and $\Omega$ is the global rotation frequency.
These parameters set the freefall Reynolds and Peclet numbers, $\Reff = \sqrt{\text{Ra}/\text{Pr}}$ and $\Peff = \text{Pr }\Reff$, and throughout this work we hold Pr = 1 so that $\Reff = \Peff$.
In standard RBC without rotation (section \ref{sec:2d_results}), we set Ek$\,= \infty$.
The extent of our numerical domain is $z = [-0.5, 0.5]$ vertically and $x, y = [-\Gamma/2, \Gamma/2]$, where $\Gamma$ is the aspect ratio.
The initial temperature profile, $T_0(z) = 0.5 - z$, is unstable and linearly decreases from a value of 1 to 0 across the domain. 
$\Delta$ is the dimensionless temperature jump across the domain; depending on our choice of boundary condition, $\Delta$ defines either a temperature or flux Rayleigh number,
\begin{equation}
\text{Ra}_{\Delta T} = \frac{g \alpha L_z^3 \Delta T_0}{\nu\kappa}, \qquad 
\text{Ra}_{\partial_z T} = \frac{g \alpha L_z^4 \partial_z T_0}{\nu\kappa}.
\end{equation}
We study both FT and TT thermal boundary conditions,
\begin{equation}
(\text{FT}): T_1 = 0 \text{ at $z$ = 0.5} \,\,\,\&\,\,\, \partial_z T_1 = 0 \text{ at $z$ = -0.5};\qquad\qquad
(\text{TT}): T_1 = 0 \text{ at $z$ = \{-0.5, 0.5\}}.
\end{equation}
In the case of FT boundaries, the temperature is nondimensionalized on the initial temperature gradient, $\Delta = L_z \partial_z T_0$, and the input Rayleigh number is a flux Rayleigh number, Ra$_{\partial_z T}$.
In the case of TT boundaries, the temperature is nondimensionalized on the initial temperature jump across the domain: $\Delta = \Delta T_0 =  T_0(z=0.5)-T_0(z=-0.5)$, and the input Rayleigh number is a temperature Rayleigh number, Ra$_{\Delta T}$.

Throughout the bulk of this work, we study two-dimensional (2D) convection where $\partial_y = v = 0$.
For comparison with the literature, we specify $\Gamma = 2$ and these simulations employ no-slip, impenetrable boundaries,
\begin{equation}
u = w = 0 \, \, \text{at}\,\,z = -0.5, 0.5.
\label{eqn:vel_bcs}
\end{equation}
The rotating cases in section \ref{sec:rotating_results} are three-dimensional (3D) tall, skinny boxes with $\Gamma = 10\lambda_c(\text{Ek})$, where $\lambda_c(\text{Ek})$ is the wavelength of convective onset at the specified value of Ek, as has been done by previous authors \cite{stellmach&all2014}. 
These rotating simulations employ stress-free, impenetrable boundaries,
\begin{equation}
\partial_z u = \partial_z v = w = 0 \, \, \text{at}\,\,z = -0.5, 0.5.
\label{eqn:vel_bcs}
\end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Ra & Nu arguments
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Nondimensional Output Quantities}
\label{sec:ra_nu_relations}
Throughout this work we will measure and report the evolved value of the Nusselt number.
We define and measure the Nusselt number instantaneously as
\begin{equation}
\text{Nu} \equiv \angles{\frac{w T - \Peff^{-1} \partial_z T}{-\Peff^{-1} \angles{\partial_z T}}}
= 1 + \Peff\frac{\angles{w T}}{-\Delta T},
\end{equation}
where $\angles{}$ represent a volume average ($\angles{A} \equiv \iint A\,dx\,dz / \Gamma$ in 2D and $\angles{A} \equiv \iiint A\,dx\,dy\,dz / \Gamma^2$ in 3D for some quantity $A$), and $\Delta T = \angles{\partial_z T}$ is the temperature difference between the top and bottom plate.
In the evolved, statistically stationary state, when TT boundaries are employed, $\text{Nu} = 1 + \Peff\angles{wT} = \text{(Evolved Flux)\Peff}$, and when FT boundaries and a flux nondimensionalization are employed, $\text{Nu} = (\Delta T)^{-1}$.
This suggests that the equilibrated state of a given convective solution is characterized by both a flux and temperature Rayleigh number whose relationship is
\begin{equation}
\text{Ra}_{\partial_z T} = \text{Ra}_{\Delta T} \text{Nu}.
\label{eqn:ra_relation}
\end{equation}
In other words, in addition to measuring the efficiency of convective heat transport, the Nusselt number is also the unit of conversion between a temperature and a flux nondimensionalization in the evolved state.

Some additional quantities of interest will be reported throughout this paper.
We will measure the evolved Peclet number of the convective flows in all sections, and in section \ref{sec:rotating_results} we will also report the value of the Rossby number.
We measure these nondimensional quantities instantaneously as
\begin{equation}
\text{Pe} = \angles{|\bm{u}|}\Peff,\qquad \text{Ro} = \angles{|\bm{\omega}|}\text{Ek }\Reff,
\end{equation}
where $|\bm{A}|$ represents the magnitude of the vector $\bm{A}$.

@@

\begin{figure}
\includegraphics[width=\textwidth]{./figs/rbc_scalar_comparisons.pdf}
\caption{ 
	(left three panels) Time traces of rolling averages over 50 freefall times of a FT (orange) and a TT (purple) simulation.
	(top left panel) The Rayleigh number, normalized by the input Ra$_{\Delta T}$ = $10^8$ value of the TT simulation.
	(middle and bottom left panels) The evolution of Nu and Pe is shown, and is normalized by the mean value measured over the last 500 freefall times of the TT simulation (reported in appendix \ref{app:table}).
	(right two panels) Compensated parameter space plots of Nu (upper) and Pe (lower) vs. Ra$_{\Delta T}$.
	The Nu vs Ra plot is compensated by $(0.138 \text{Ra}_{\Delta T}^{0.285})$, which was the best-fit reported by ref.~\cite{johnston&doering2009}.
	The Re vs Ra plot is compensated by a Ra$_{\Delta T}^{1/2}$ law, which is the anticipated scaling of the Peclet number \cite{ahlers&all2009}.
	The time evolution of the FT case is shown as an orange trace with the arrows showing the sense of time.
	Purple circles show our measured values of Nu in TT simulations (reported in appendix \ref{app:table}); error bars show the standard deviation of the sample mean and are smaller than the marker in all cases.
	The orange star in each plot corresponds to the TT case whose time evolution is shown on the left.
	Black crosses show comparison TT simulations as reported by ref.~\ref{zhu&all2018}.
\label{fig:rbc_scalar_comparisons} }
\end{figure}

In Fig.~\ref{fig:rbc_scalar_comparisons}, we describe the evolution of a FT simulation which is characterized by Ra$_{\partial_z T}$ = 2.61$\,\times 10^9$.
The left panels of Fig.~\ref{fig:rbc_scalar_comparisons} compare this simulation to a TT case with Ra$_{\Delta T} = 10^8$.
The FT case is displayed in orange, and the TT case is displayed in purple; the x-axis of the left panels shows simulation time, in freefall units, with the time of the simulation's end subtracted from it (such that $x = 0$ corresponds to the end of the simulation).
In the top-left panel, we compare the evolution of the Rayleigh number of these simulations: temperature Rayleigh numbers, Ra$_{\Delta T}$ are displayed as solid lines, and flux Rayleigh numbers, Ra$_{\partial_z T}$ are shown as dash-dot lines.
The value of Ra$_{\Delta T}$ takes thousands of time units to reach its final value for the FT simulation, and this final value corresponds to the input value of the equivalent TT case.
On the other hand, the value of Ra$_{\partial_z T}$ for the TT case nearly instantaneously reaches its final value, which corresponds to the input value for the FT simulation.
This discrepancy in evolution timescales, where TT simulations evolve quickly and FT simulations evolve slowly, is also seen in the equilibration of the Nusselt number (middle panel) and Peclet number (bottom panel).
All time traces displayed are rolling averages over 50 freefall times, in order to reduce the variance of the plotted quantities.

In the right panels of Fig.~\ref{fig:rbc_scalar_comparisons}, we plot compensated scaling plots of Nu and Pe vs Ra$_{\Delta T}$.
Over the course of its thermal relaxation, the FT case performs a sweep through Ra$_{\Delta T}$ parameter space.
During this parameter space sweep, the FT simulation seems to trace out the expected scaling law of Nu vs.~Ra displayed by TT simulations and which has been reported by previous authors.
However, we find that the value of Pe measured in the FT simulation through its relaxation  is larger than the value of the Peclet number in comparison TT simulations until it converges to its final state.
These traces through parameter space demonstrate the importance of waiting until a FT simulation has reached its equilibrated state.
During the rundown, the dynamics in FT simulations are constantly evolving, and also they display more vigorous convection than in equivalent converged states, suggesting that the dynamics do not immediately ``forget'' the higher-Ra$_{\Delta T}$ state that they were previously in during the parameter space sweep.
Both of these effects make interpretation of their results difficult until the final, equilibrated state.

\begin{figure}
\includegraphics[width=\textwidth]{./figs/rbc_restart_description.pdf}
\caption{ 
	(left three panels) Time traces of rolling averages over 25 freefall times of a simulation which starts with TT boundary conditions and then is switched to FT boundary conditions.
	The time at which we switch from TT to FT boundaries is noted by the vertical black line.
	(top left panel) The Rayleigh number's evolution over time is shown; Ra$_{\partial_z T}/(2.61\times 10^9)$ is shown as a dashed-dot line, while Ra$_{\Delta T}/10^8$ is shown as a solid line.
	The mean value of the bottom boundary's temperature gradient (middle panel) and temperature (bottom panel) are consistently nondimensionalized and displayed, showing the change in the enforced boundary condition.
	In the TT initial state, the temperature is held constant at a value of 1 and the temperature derivative fluctuates around a value of $\angles{\text{Nu}}$.
	In the FT final state, the temperature derivative is held constant at a value of -1 and the temperature value fluctuates around a value of $\angles{\text{Nu}}^{-1}$.
	(right four panels) Probability distribution functions of dynamics at all spatial points in the domain sampled once each freefall time for a total of 500 freefall times are shown.
	We display the temperature field (upper left), enstrophy (upper right), nonlinear convective enthalpy flux (bottom left), and vertical velocity (bottom right).
	In each plot, we compare the PDF of the FT case which thermally relaxed (in Fig.~\ref{fig:rbc_scalar_comparisons}) to the PDF of the ``t-to-m'' (TT-to-FT) case which is drawn from dynamics in the grey shaded region displayed in the left three panels here.
\label{fig:rbc_restart_description} }
\end{figure}

>>>>

\begin{abstract}
Astrophysical simulations of convection frequently impose different thermal boundary conditions at the top and the bottom of the domain in an effort to more accurately reflect the natural system being modeled.
In this work, we study \RB convection (RBC) to show that the use of these mixed (FT) thermal boundary conditions imposes a long thermal rundown on convective systems which is not experienced by the more classical system where the temperature is fixed at the top and bottom of the domain (TT).
In the evolved state, the mean behavior of an FT simulation corresponds to an equivalent simulation with TT boundaries, and the fast evolution of TT simulations can be taken advantage of to rapidly relax FT simulations.
We show that these findings carry over to more complicated problems through a brief examination of rotating convection.
We furthermore find that FT boundaries introduce minor asymmetries into the flow fields, with the fixed flux boundary producing more extreme events than the fixed temperature boundary, but that these asymmetries do not appreciably affect the bulk flows.
We conclude that thermal relaxation occurs in two stages: (1) changes to the experimental energy reservoir and (2) changes to the stratification of the experiment.
Through the proper choice of boundary conditions or initial conditions, the first of these stages can be bypassed, and the second stage seems to be irrelevant for RBC.
\end{abstract}
\maketitle

@@

\section{Introduction}
\label{sec:introduction}
Convection is a crucial heat transport mechanism in the atmospheres and interiors of stars and planets.
Numerical simulations are a commonly-used tool in studies into the nature of convection.
These studies range from examinations of convection in the simplified Boussinesq approximation \cite{spiegel&veronis1960, ahlers&all2009, plumley&julien2019} to highly complex ``dynamo simulations'' which include magnetism and atmospheric density stratification \cite{charbonneau2014, toomre2019}.
In these simulations, convection is fundamentally driven by some combination of imposed boundary conditions and internal heating profiles \cite{goluskin2015}.
One common choice of thermal boundary conditions in astrophysical convection \cite{glatzmaier&gilman1982, hurlburt&all1986, cattaneo&all1990, featherstone&hindman2016a, korre&all2019, wood&brummell2018, kapyla&all2019} is to fix the flux at the bottom boundary and to fix the value of a thermodynamic quantity (e.g., temperature or entropy) at the top boundary.
However, in Boussinesq studies of \RB convection, the most frequently-utilized choice of boundary conditions is to fix the temperature at both boundaries.
We are unaware of any study which has examined the consequences of imposing the ``mixed'' boundaries that are frequently favored in astrophysical convection studies.

In this work, we examine how the choice of using ``mixed'' boundaries affects the evolved nonlinear convective state in the simplest possible model: \RB convection (RBC) under the Boussinesq approximation.
In RBC, temperature is the only thermodynamic quantity and throughout this work we will refer to the choice of fixing the flux at the bottom and temperature at the top as ``FT'' boundary conditions.
We will refer to the common choice of fixing temperature at both boundaries as ``TT'' boundaries, and fixing the flux at both boundaries as ``FF'' boundaries\footnote{Note, in ref.~\cite{goluskin2015}, our TT, FF, and FT are repsectively called RB1, RB2, and RB3.}.
It is generally assumed that FT and FF boundaries should fundamentally behave similarly \cite{goluskin2015}, and the behavior of FF boundaries is well-known \cite{otero&all2002, johnston&doering2009}.
The scaling of the convective heat transport, quantified by the Nusselt number, as a function of increased convective driving, quantified by the Rayleigh number, has been shown to be equivalent for FF and TT boundaries \cite{johnston&doering2009}, and it is natural to assume that FT should fall on the same scaling laws.
However, FT boundaries introduce complexities into the convective solution which neither FF or TT boundaries are exposed to.
First, the evolved mean temperature of a simulation with FT boundaries differs from the initial mean temperature, and therefore the thermal reservoir of the convective system must evolve over time \cite{anders&all2018}.
Second, FT boundary conditions are fundamentally asymmetric, and it is unclear if these asymmetries affect the evolved convective solution.

In this paper, we investigate the time evolution and nature of asymmetries in \RB covection when FT boundary conditions are imposed, and we compare evolved FT solutions to the most commonly studied TT solutions.
We find that the thermal evolution and relaxation of FT systems is very long compared to TT systems, where it is nearly instantaneous.
However, this long thermal evolution can be bypassed by using the results of TT simulations as initial conditions for FT simulations.
We also find that during their thermal relaxation, FT simulations simulations perform a sweep through parameter space, effectively sampling dynamics at various values of the Rayleigh number over their evolution.
Finally, our results suggest that the choice of FT boundaries imposes some asymmetries on the convective flows, but that these asymmetries do not importantly change the mean convective state when compared to TT siulations.

We present these findings as follows.
In section \ref{sec:simulations}, we describe our simulation setup and numerical methods.
In section \ref{sec:2d_results}, we first describe our findings with respect to the time evolution of FT systems, and then describe the asymmetries in these systems.
In section \ref{sec:rotating_results}, we show that these findings carry over to a more complex system: rotating \RB convection.
Finally, in section \ref{sec:discussion}, we summarize our findings and briefly describe the implications of this work for the field of astrophysical convection.

@@

\section{Simulation Details}
\label{sec:simulations}
We study incompressible \RB convection under a freefall nondimensionalization as we have done previously \cite{anders&all2018}; for details of the nondimensionalization, we refer readers to that previous work.
In section \ref{sec:rotating_results} we study convection which includes the effects of vertical global rotation \cite{julien&all1996}, so here we include the Coriolis term in the momentum equation for generality.
The Boussinesq equations of motion are
\begin{align}
\Div{\bm{u}} &= 0
	\label{eqn:incompressible}
\\
\frac{\partial \bm{u}}{\partial t} + \left(\bm{\omega} + \frac{1}{\text{Ek }\Reff}\hat{z}\right)\times\bm{u} 
&= - \grad \varpi + T_1\hat{z} - \frac{1}{\Reff}\grad\times\bm{\omega},
	\label{eqn:bouss_momentum}
\\
\frac{\partial T_1}{\partial t}  + \bm{u}\cdot\grad T_1 + w \frac{\partial T_0}{\partial z} 
&= \frac{1}{\Peff}\grad^2 T_1,
	\label{eqn:bouss_energy}
\end{align}
where $\bm{u} = (u, v, w)$ is the velocity, $T = T_0(z) + T_1(x, y, z, t)$ is the temperature (where $T_0$ is the initial profile and $T_1$ are the fluctuations around that profile), $\varpi$ is the reduced kinematic pressure \cite{anders&all2018} which enforces the incompressibility constraint, and $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.
The dimensionless control parameters are the Rayleigh (Ra), Prandtl (Pr), and Ekman (Ek) numbers, defined respectively as
\begin{equation}
\text{Ra} = \frac{g \alpha L_z^3 \Delta}{\nu\kappa} = \frac{(L_z\,v_{\text{ff}})^2}{\nu\kappa}, \qquad \text{Pr} = \frac{\nu}{\kappa}, \qquad \text{Ek} = \frac{\nu}{2\Omega L_z^2},
\end{equation}
where $g$ is the gravity, $\alpha$ is the coefficient of thermal expansion, $L_z$ is the domain depth, $\nu$ and $\kappa$ are respectively the viscous and thermal diffusivity, $\Omega$ is the global rotation frequency, and $\Delta$ is the nondimensional temperature scale.
These parameters set the freefall Reynolds and P\'{e}clet numbers, 
\begin{equation}
\Reff = \sqrt{\frac{\text{Ra}}{\text{Pr}}},\qquad
\Peff = \text{Pr }\Reff,
\end{equation}
and throughout this work we hold Pr = 1 so that $\Reff = \Peff$.
In standard RBC without rotation (section \ref{sec:2d_results}), we set Ek$\,= \infty$.
The extent of our numerical domain is vertically $z = [-0.5, 0.5]$ and horizontally $x, y = [-\Gamma/2, \Gamma/2]$, where $\Gamma$ is the aspect ratio.
The initial temperature profile, $T_0(z) = 0.5 - z$, is unstable and linearly decreases from a value of 1 to 0 across the domain. 
Depending on our choice of boundary condition, $\Delta$ is set by either the temperature jump across the domain or by the temperature gradient length scale.
In the case of the former, Ra$_{\Delta T}$ is a temperature Rayleigh number; in the case of the latter, Ra$_{\partial_z T}$ is a flux Rayleigh number,
\begin{equation}
\text{Ra}_{\Delta T} = \frac{g \alpha L_z^3 \Delta T_0}{\nu\kappa}, \qquad 
\text{Ra}_{\partial_z T} = \frac{g \alpha L_z^4 \partial_z T_0}{\nu\kappa}.
\end{equation}
In this work, we study both FT and TT thermal boundary conditions,
\begin{equation}
(\text{FT}): \partial_z T_1 = 0 \text{ at $z$ = -0.5} \,\,\,\&\,\,\, T_1 = 0 \text{ at $z$ = 0.5};\qquad\qquad
(\text{TT}): T_1 = 0 \text{ at $z$ = \{-0.5, 0.5\}}.
\end{equation}
In the case of FT boundaries, $\Delta = L_z \partial_z T_0$, and the input Rayleigh number is Ra$_{\partial_z T}$, while for TT boundaries, $\Delta = \Delta T_0 =  T_0(z=0.5)-T_0(z=-0.5)$, and the input Rayleigh number is Ra$_{\Delta T}$.

In section \ref{sec:2d_results}, we study two-dimensional (2D) convection where $\partial_y = v = 0$.
For comparison with the literature, we specify $\Gamma = 2$ and these simulations employ no-slip, impenetrable boundaries,
\begin{equation}
u = w = 0 \, \, \text{at}\,\,z = \{-0.5, 0.5\}.
\label{eqn:vel_bcs}
\end{equation}
The rotating cases in section \ref{sec:rotating_results} are three-dimensional (3D) tall, skinny boxes with $\Gamma = 10\lambda_c(\text{Ek})$, where $\lambda_c(\text{Ek})$ is the wavelength of convective onset at the specified value of Ek, as has been done by previous authors \cite{stellmach&all2014}. 
For the cases studied here at Ek = $10^{-6}$, $\lambda_c(10^{-6}) = 4.81 \times 10^{-2}$.
These rotating simulations employ stress-free, impenetrable boundaries,
\begin{equation}
\partial_z u = \partial_z v = w = 0 \, \, \text{at}\,\,z = \{-0.5, 0.5\}.
\label{eqn:vel_bcs}
\end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Ra & Nu arguments
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Nondimensional Output Quantities}
\label{sec:ra_nu_relations}
Throughout this work we will measure and report the evolved value of the Nusselt number (Nu).
We define and measure Nu instantaneously as
\begin{equation}
\text{Nu} \equiv \angles{\frac{w T - \Peff^{-1} \partial_z T}{-\Peff^{-1} \angles{\partial_z T}}}
= 1 + \Peff\frac{\angles{w T}}{-\Delta T},
\end{equation}
where $\angles{}$ represent a volume average ($\angles{A} \equiv \iint A\,dx\,dz / \Gamma$ in 2D and $\angles{A} \equiv \iiint A\,dx\,dy\,dz / \Gamma^2$ in 3D for some quantity $A$), and $\Delta T = \angles{\partial_z T}$ is the temperature difference between the top and bottom plate.
In an evolved, statistically stationary state, $\left.\text{Nu} = 1 + \Peff\angles{wT} = \partial_z T\right|_{z = \{-0.5, 0.5\}}$ when TT boundaries are employed, and $\text{Nu} = (\Delta T)^{-1}$ when FT boundaries and a flux nondimensionalization are employed.
This implies that Nu is the conversion between a temperature and flux nondimensionalization such that the equilibrated state of any convective solution is characterized by Ra$_{\Delta T}$ and Ra$_{\partial_z T}$ according to
\begin{equation}
\text{Ra}_{\partial_z T} = \text{Ra}_{\Delta T} \text{Nu}.
\label{eqn:ra_relation}
\end{equation}

Throughout this work, we will also measure the evolved P\'{e}clet number (Pe) and in section \ref{sec:rotating_results} we will measure the Rossby number (Ro).
These nondimensional quantities are defined as
\begin{equation}
\text{Pe} = \angles{|\bm{u}|}\Peff,\qquad \text{Ro} = \angles{|\bm{\omega}|}\text{Ek }\Reff,
\end{equation}
where $|\bm{A}|$ represents the magnitude of the vector $\bm{A}$.

@@

\begin{figure}
\includegraphics[width=\textwidth]{./figs/rbc_scalar_comparisons.pdf}
\caption{ 
	(left three panels) Time traces of rolling averages over 100 freefall times of a FT (orange) and a TT (purple) simulation.
	(top left panel) Ra, normalized by the input Ra$_{\Delta T}$ = $10^9$ value of the TT simulation.
	(middle and bottom left panels) The evolution of Nu and Pe is shown, and is normalized by the mean value measured over the last 500 freefall times of the TT simulation (reported in appendix \ref{app:table}).
	(right two panels) Compensated parameter space plots of Nu (upper) and Pe (lower) vs. Ra$_{\Delta T}$.
	The Nu vs Ra.~plot is compensated by $(0.138 \text{Ra}_{\Delta T}^{0.285})$, which was the best-fit reported by ref.~\cite{johnston&doering2009}.
	The Re vs Ra.~plot is compensated by a Ra$_{\Delta T}^{1/2}$ law, which is the anticipated scaling of Pe \cite{ahlers&all2009}.
	The orange trace shows the time evolution of the FT case from the left panels with the arrows showing the sense of time.
	The yellow trace shows the evolution of an FT case with Ra$_{\Delta T} = 10^8$.
	Purple circles show our measured values of Nu in TT simulations (reported in appendix \ref{app:table}); error bars show the standard deviation of the sample mean and are smaller than the marker in all cases.
	The purple circles filled in with yellow and orange are the TT comparisons for the evolved states of the two FT cases.
	Black crosses show comparison TT simulations as reported by ref.~\cite{zhu&all2018}.
\label{fig:rbc_scalar_comparisons} }
\end{figure}

In the left panels of Fig.~\ref{fig:rbc_scalar_comparisons}, we display the evolution of a FT simulation with Ra$_{\partial_z T}$ = 4.83$\,\times 10^{10}$ (orange lines) and a TT simulation with Ra$_{\Delta T} = 10^9$ (purples lines).
Simulation time in nondimensional freefall units is shown on the x-axis; each simulation's end time, $t_{\text{final}}$, is subtracted so that the final evolved states can be more directly compared, and so that $x = 0$ corresponds to the end of the simulation.
The lines shown are rolling averages taken over 100 freefall time units.
In the top-left panel, the evolution of Ra$_{\Delta T}$ and Ra$_{\partial_z T}$ is shown in each simulation.
In the FT simulation, Ra$_{\Delta T}$ evolves towards its final value over thousands of simulation time units; this final value corresponds to the input value of the equivalent TT case.
In comparison, Ra$_{\partial_z T}$ for the TT case nearly instantaneously reaches its final value, which corresponds to the input value for the FT simulation.
This discrepancy in evolution timescales, where TT simulations evolve quickly and FT simulations evolve slowly, is also seen in the equilibration of Nu (middle panel) and Pe (bottom panel).

The right panels of Fig.~\ref{fig:rbc_scalar_comparisons} show that the evolution of Ra$_{\Delta T}$ in FT simulations is akin to a sweep through Ra$_{\Delta T}$ parameter space.
The orange lines show the evolution of the Ra$_{\partial_z T} = 4.83 \times 10^{10}$ case shown on the left, and the yellow lines show the evolution of a Ra$_{\partial_z T} = 2.61 \times 10^{9}$.
The arrow give the sense of time in the simulations.
For comparison, we have computed TT simulations throughout this parameter space (purple circles) and we have overplotted the reported results of ref.~\cite{zhu&all2018}.
The purple circles filled with orange and yellow circles respectively show the comparison TT simulations for the evolved FT simulations.
In the upper panel, we show a compensated scaling plot for Nu vs.~Ra$_{\Delta T}$, compensated by the best fit reported in ref.~\cite{johnston&doering2009}.
The lower panel is a compensated scaling plot of Pe vs~Ra$_{\Delta T}$, compensated by the expected scaling \cite{ahlers&all2009}.
We find that the FT simulations are more turbulent (higher Pe) and carry marginally more flux (higher Nu) than comparable TT simulations as they sweep through this parameter space.
The dynamics in FT simulations evolve slowly during the rundown, and these traces demonstrate the importance of waiting until a FT simulation has reached its equilibrated state before sampling and analyzing the nonlinear convective state.
Furthermore, the heightened values of Nu and especially Pe suggest that the dynamics do not immediately ``forget'' the higher-Ra$_{\Delta T}$ state that they recently timestepped through on their way to achieving thermal relaxation.

\begin{figure}
\includegraphics[width=\textwidth]{./figs/rbc_restart_description.pdf}
\caption{ 
	(left three panels) Time traces of rolling averages over 25 freefall times of a simulation with Ra$_{\Delta T} = 10^9$ which starts with TT boundary conditions and then is switched to FT boundary conditions.
	The time at which we switch from TT to FT boundaries is noted by the vertical black line.
	(top left panel) The evolution of Ra over time is shown; Ra$_{\partial_z T}/(48.3\times 10^{10})$ is shown as a dashed-dot line, while Ra$_{\Delta T}/10^9$ is shown as a solid line.
	The mean value of the bottom boundary's temperature gradient (middle panel) and temperature (bottom panel) are consistently nondimensionalized and displayed, showing the change in the enforced boundary condition.
	In the TT initial state, the temperature is held constant at a value of 1 and the temperature derivative fluctuates around a value of $\text{Nu}$.
	In the FT final state, the temperature derivative is held constant at a value of -1 and the temperature value fluctuates around a value of $\text{Nu}^{-1}$.
	(right four panels) Probability distribution functions of dynamics at all spatial points in the domain sampled once each freefall time for a total of 500 freefall times are shown (the grey shaded region in the left three panels).
	We display the temperature field (upper left), enstrophy (upper right), nonlinear convective enthalpy flux (bottom left), and vertical velocity (bottom right).
	In each plot, we compare the PDF of the FT case which thermally relaxed (in Fig.~\ref{fig:rbc_scalar_comparisons}; green PDF) to the PDF of the TT-to-FT case (grey PDF).
\label{fig:rbc_restart_description} }
\end{figure}
